---
title: "AN588-Week-2-chuhan"
author: "Author: Lia"
date: "Date: 2023-09-16"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Homework1
Load the stringr package first. 
```{r}
library(stringr)
```

### Challenge 1
```{r}
v <-str_split("Stately, plump Buck Mulligan came from the stairhead, bearing a bowl of lather on which a mirror and a razor lay crossed.", " ")
v2 <- v[[1]]
v2[seq(from=3, to=22, by=3)]
```
Challenge 1 complete :)

### Challenge 2
Define the matrix first.
```{r}
m <- matrix(data=1:80, nrow=8, ncol=10, byrow=FALSE)
m
```
1. Extract the 2^nd^, 3^rd^, and 6^th^ columns. Assign to the variable **x1**.
```{r}
x1 <- m[,c(2, 3, 6)]
x1
```
2. Extract the 6^th^ to 8^th^ row. Assign to the variable **x2**. 
```{r}
x2 <- m[c(6:8),]
x2
```
3. Extract the elements from row 2, column 2 to row 6, column 9. Assign to the variable **x3**. 
```{r}
x3 <- m[2:6, 2:9]
x3
```
Challenge 2 complete :)

### Challenge 3
Create the matrix first. 
```{r}
a <- array(data=400:1, dim=c(5, 5, 4, 4))
a
```
Then run the code given in Module 4. 
```{r}
a[1, 1, 1, 2]
```
```{r}
a[2, 3, 2, ]
```
```{r}
a[1:5, 1:5, 3, 3]
```
About the overwriting part, basically you overwrite the value you have reassigned. 

For example, m[7,1]<-564 will lead to the value at row 7 column 1 get overwritten as 564. 

This applies to similar operations listed in Module 4.
```{r}
m[2:5, 4:8] <- 1
m
```
The values from row 2, column 4 to row 5, column 8 get overwritten as 1. 

Challenge 3 complete :)

### Challenge 4
Create the whole list for Primates.
```{r}
Lemuroidea <- c("Cheirogaleidae", "Lepilemuridae", "Indriidae", "Lemuridae",
    "Daubentoniidae")
Lorisoidea <- c("Lorisidae", "Galagidae")
Tarsioidea <- c("Tarsiidae")
Platyrrhini <- c("Cebidae", "Atelidae", "Pitheciidae")
Catarrhini <- c("Cercopithecidae", "Hylobatidae", "Hominidae")
Anthropoidea <- list(Platyrrhini, Catarrhini)
names(Anthropoidea) <- list("Platyrrhini", "Catarrhini")
Haplorhini <- list(Anthropoidea, Tarsioidea)
names(Haplorhini) <- list("Anthropoidea", "Tarsioidea")
Strepsirhini <- list(Lemuroidea, Lorisoidea)
names(Strepsirhini) <- list("Lemuroidea", "Lorisoidea")
Primates <- list(Haplorhini, Strepsirhini)
names(Haplorhini) <- list("Anthropoidea", "Tarsioidea")
names(Primates) <- list("Haplorihini", "Strepsirhini")
Primates
```
I wonder if there is any method to simplify the code or improve it. 

The code above is just repeating the code provided in Module 4. 

Anyway, Challenge 4 complete :)

### Challenge 5

1. Create the matrix.   
```{r}
m3 <- matrix(data=c(3, 0, 1 ,23, 1, 2, 33, 1, 1, 42, 0, 1, 41, 0, 2), nrow=5, ncol=3, byrow=TRUE)
m3
```
2. Coerce the matrix to a data frame. 
```{r}
df <- data.frame(m3)
df
```
3. Coerce the 2^nd^ column to be logical-valued, and 3^rd^ column to be factor-valued. 
```{r}
df2 <- data.frame(Col1=c(df$X1), Col2=c(as.logical(df$X2)), Col3=c(as.factor(df$X3)))
df2
```
4. Show the data type of each variable in the dataframe. 
```{r}
str(df2)
```
According to the result of str() command, the data types are converted successfully. 

Challenge 5 complete :)

Homework 1 Complete :D